Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-07-26 ms.tex
Update on Overleaf.

We include a UV background, tabulated metal line cooling, and a 9 species non-equilibrium chemistry solver using \textsc{Grackle} \citep{GrackleMethod}. Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling a
%  removed to try and limit citation count
    %\cite{Salpeter1955} 
Salpeter IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range. For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection. FUV and LW band radiation are both taken to be optically thin, with local (cell-by-cell) attenuation alone. Ionizing radiation is followed using radiative transfer, as discussed below. Stellar lifetimes, surface gravity, effective temperature, and radii are set by the initial stellar mass and metallicity through interpolation over the PARSEC \citep{Bressan2012} zero age main sequence values. These values for surface gravity, effective temperature, and radii are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanzHubeny2003} grid. We only follow the radiation from stars with masses above 8~M$_{\odot}$. 
%tellar wind and supernovae mass loss are determined with the  NuGrid yield tables for $M_* < 25$~M$_{\odot}$ and from Slemer et. al. (in prep) for $M_* > 25$~M$_{\odot}$.

@@

\textbf{New text (AE needs work not done yet): Finally, we quantify these findings in Figure~\ref{fig:vertical profiles}, showing the volume-weighted average number density (left), temperature (middle) and hydrogen ionization fraction (right) as a function of distance above/below the disk of our galaxy at the same time as Figure~\ref{fig:panel2}. Over the sampled heights, the gas outside the disk of our fiducial simulation is lower density, higher temperature, and has a higher ionization fraction at all heights. }

\textbf{New text: As shown in Figure~\ref{fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy. The winds in our fiducial simulation carry nearly all of the metals produced out from the disk of our galaxy. This is the only run in agreement with observations of Local Group dwarf galaxies, both dSph's \citep{Kirby2011} and the gaseous, star forming Local Group dwarf galaxy Leo P \citep{McQuinn2015}, with metal ejection fractions of up to 95\%. This is in stark contrast to the $\sim$30\% retention fraction in our shortrad simulation. This would also influence the chemical enrichment of neighboring galaxies, given the significant differences in metal ejection past the virial radius between these two runs. Clearly the effects of feedback on observable chemical properties of galaxies is a key descriminator among models.}

>>>>

We include a UV background, tabulated metal line cooling, and a 9 species non-equilibrium chemistry solver using \textsc{Grackle} \citep{GrackleMethod}. Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling a \cite{Salpeter1955} Salpeter IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range. For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection. FUV and LW band radiation are both taken to be optically thin, with local (cell-by-cell) attenuation alone. Ionizing radiation is followed using radiative transfer, as discussed below. Stellar lifetimes, surface gravity, effective temperature, and radii are set by the initial stellar mass and metallicity through interpolation over the PARSEC \citep{Bressan2012} zero age main sequence values. These values for surface gravity, effective temperature, and radii are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanzHubeny2003} grid. We only follow the radiation from stars with masses above 8~M$_{\odot}$. 
%tellar wind and supernovae mass loss are determined with the  NuGrid yield tables for $M_* < 25$~M$_{\odot}$ and from Slemer et. al. (in prep) for $M_* > 25$~M$_{\odot}$.

@@

\textbf{New text: Finally, we quantify these findings in Figure~\ref{fig:vertical profiles}, showing the volume-weighted average number density (left), temperature (middle) and hydrogen ionization fraction (right) as a function of distance above/below the disk of our galaxy at the same time as Figure~\ref{fig:panel2}. The gas outside the disk of our fiducial simulation is lower density, higher temperature, and has a higher ionization fraction at all points above the disk. The shortrad simulation, which lacks both the enhanced SNR of the noRT run and the long-range ionizing radiation effects, of the fiducial simulation, maintains a denser, cooler, more neutral shell of gas above the disk, preventing significant outflows.}

\textbf{New text: As shown in Figure~\ref{fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy. The winds in our fiducial simulation carry nearly all of the metals produced out from the disk of our galaxy. This is the only run in agreement with observations of Local Group dwarf galaxies, both dSph's \citep{Kirby2011} and the gaseous, star forming Local Group dwarf galaxy Leo P \citep{McQuinn2015}, with metal ejection fractions of up to 95\%. This is in stark contrast to the $\sim$30\% retention fraction in our shortrad simulation. This would also influence the chemical enrichment of neighboring galaxies, given the significant differences in metal ejection past the virial radius between these two runs. Clearly the effects of feedback on observable chemical properties of galaxies is a key discriminator among models.}
